The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-13 analysis/paper/paper.qmd
Remove white spaces

# Load analysis functions ----
devtools::load_all(".")

@@

# Join text with the metadata file  
emu <- left_join(emu_raw, emu_metadata, by = "ID")

@@

mermaid("
graph LR
    A[Data collection]-->B[Pre-processing]
    B-->C[Information extraction]
    C-->D[Visualisation]
    C-->B
    D-->E[Results]
")

@@

# Unnest words and remove words of one and two letters
emu_words <- emu |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>  # remove punctuation, convert to lower-case, separate all words
  anti_join(tidytext::stop_words, by = "word") |>  # remove stop words
  mutate(word = textstem::lemmatize_words(word))  # lemmatise words

@@

```{r}
topicToFilter <- 6  # you can set this manually ...
# ... or have it selected by a term in the topic name (e.g. 'children')
topicToFilter <- grep('river', topic_names)[1] 
topicThreshold <- 0.2
selectedDocumentIndexes <- which(theta[, topicToFilter] >= topicThreshold)
filteredCorpus <- emu_theses[selectedDocumentIndexes,]
# show length of filtered corpus
filteredCorpus
```

@@

# Plot topic proportions per year
vizDataFrameWithYear |> 
  ggplot(aes(x = factor(year), y = value, fill = topic)) + 
  geom_bar(stat = "identity", position = "fill") +
  scale_fill_viridis_d(name = "Topics") +
  xlab("Graduation year") +
  ylab("Proportion of topics") +
  labs(title = "Topic proportions per year")

@@

```{r top-words-document}
# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_words, top_n = 10)
```

```{r top-words-corpus}
# Which are the top n most frequently used words in all theses?
# TODO add `topic` to `fill` aesthetic
n = 50
get_top_words_per_corpus(data = emu_words, top_n = n) |>
  ggplot(aes(reorder(word, n), n)) +
  geom_col(fill = "orange") +
  geom_text(aes(label = n), size = 2, hjust = 1.1) +
  coord_flip() +
  xlab("Word") +
  ylab("Frequency") +
  labs(title = paste0("Top ", n, " most used words in the corpus of theses")) +
  theme_minimal() +
  theme(panel.grid = element_blank())
```

@@

bigram_counts
bigram_stem_counts
```

```{r}
## Trigrams
emu_trigrams <- emu |> 
  get_ngrams(n = 3, title_col = "title", text_col = "text_raw")

@@

trigram_tf_idf

## Show network of bigrams
bigram_graph <- bigram_counts |> 
  filter(n > 100) |> 
  graph_from_data_frame()

@@

```{r}
# Preview term frequency distributions in a subset of theses

emu_words_count <- emu_words |> 
  count(title, word, sort = TRUE) |> 
  ungroup()

@@

# To what extent do words co-occur with other words?
tidy_pmi <- get_pmi(emu, title_col = "title", text_col = "text_clean")

@@

# Determine word vectors using SVD, a method for dimensionality reduction
tidy_word_vectors <- tidy_pmi |> 
  widely_svd(
    item1, item2, pmi,
    nv = 100, maxit = 1000
  )

@@

# Calculate nearest neighbours of a given word
tidy_word_vectors |> 
  nearest_neighbors("resilience")

@@

# The first n components with top words found in the corpus of theses
visualise_first_n_components(tidy_word_vectors, 24, 12)

@@

dim(doc_matrix)

doc_matrix

>>>>

# Load analysis functions ----
devtools::load_all(".")
```

@@

# Join text with the metadata file  
emu <- left_join(emu_raw, emu_metadata, by = "ID")
```

@@

mermaid("
graph LR
    A[Data collection]-->B[Pre-processing]
    B-->C[Information extraction]
    C-->D[Visualisation]
    C-->B
    D-->E[Results]
")
```

@@

# Unnest words and remove words of one and two letters
emu_words <- emu |> 
  select(title, text_clean) |> 
  unnest_tokens(output = word, input = text_clean) |>  # remove punctuation, convert to lower-case, separate all words
  anti_join(tidytext::stop_words, by = "word") |>  # remove stop words
  mutate(word = textstem::lemmatize_words(word))  # lemmatise words
```

@@

topicToFilter <- 6  # you can set this manually ...
# ... or have it selected by a term in the topic name (e.g. 'children')
topicToFilter <- grep('river', topic_names)[1] 
topicThreshold <- 0.2
selectedDocumentIndexes <- which(theta[, topicToFilter] >= topicThreshold)
filteredCorpus <- emu_theses[selectedDocumentIndexes,]
# show length of filtered corpus
filteredCorpus
```

@@

# Plot topic proportions per year
vizDataFrameWithYear |> 
  ggplot(aes(x = factor(year), y = value, fill = topic)) + 
  geom_bar(stat = "identity", position = "fill") +
  scale_fill_viridis_d(name = "Topics") +
  xlab("Graduation year") +
  ylab("Proportion of topics") +
  labs(title = "Topic proportions per year")
```

@@

```{r top-words-document}

# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_words, top_n = 10)
```

```{r top-words-corpus}

# Which are the top n most frequently used words in all theses?
# TODO add `topic` to `fill` aesthetic
n = 50
get_top_words_per_corpus(data = emu_words, top_n = n) |>
  ggplot(aes(reorder(word, n), n)) +
  geom_col(fill = "orange") +
  geom_text(aes(label = n), size = 2, hjust = 1.1) +
  coord_flip() +
  xlab("Word") +
  ylab("Frequency") +
  labs(title = paste0("Top ", n, " most used words in the corpus of theses")) +
  theme_minimal() +
  theme(panel.grid = element_blank())
```

@@

bigram_counts
bigram_stem_counts

## Trigrams
emu_trigrams <- emu |> 
  get_ngrams(n = 3, title_col = "title", text_col = "text_raw")

@@

trigram_tf_idf
```

```{r}
## Show network of bigrams
bigram_graph <- bigram_counts |> 
  filter(n > 100) |> 
  graph_from_data_frame()

@@

# Preview term frequency distributions in a subset of theses
emu_words_count <- emu_words |> 
  count(title, word, sort = TRUE) |> 
  ungroup()

@@

# To what extent do words co-occur with other words?
tidy_pmi <- get_pmi(emu, title_col = "title", text_col = "text_clean")
```

@@

# Determine word vectors using SVD, a method for dimensionality reduction
tidy_word_vectors <- tidy_pmi |> 
  widely_svd(
    item1, item2, pmi,
    nv = 100, maxit = 1000
  )
```

@@

# Calculate nearest neighbours of a given word
tidy_word_vectors |> 
  nearest_neighbors("resilience")
```

@@

# The first n components with top words found in the corpus of theses
visualise_first_n_components(tidy_word_vectors, 24, 12)
```

@@

dim(doc_matrix)
```
